Specific taxa differentiate proximal and distal microbiota in the unprepped

### 2017-06-19 submission/manuscript.Rmd
almost done
final tweaks

---
title: '*Specific taxa differentiate proximal and distal
  microbiota in the unprepped human colon*'
csl: mbio.csl
fontsize: 11pt
output:
  html_document: default
  pdf_document:
    includes: null
    keep_tex: yes
  word_document: default
geometry: margin=1.0in
bibliography: references.bib
---
\vspace{35mm}

@@

#### Random Forest classification models identify important OTUs on each side
To identify OTUs that were distinct at each biogeographical site, we constructed several Random Forest models built on OTU abundances. We built the first model to classify the lumen versus mucosal samples for the right and left sides, independently (Figure 4A). The constructed model used ((Xopt)) features for the right and ((Xopt)) for the left. The models performed well when classifying these samples (AUC = 0.797 and AUC = 0.980, respectively). The OTUs that were most predictive of each site are identified by their greatest mean decrease in accuracy when removed from the model. For distinguishing the right lumen and mucosa, OTUs from the _Bacteriodes_, _Actinomyces_, _Psuedomonas_ and two OTUs from the _Enterobacteraceae_ genera were differentially abundant (Figure 4B). The model classifying the left lumen and mucosa identified OTUs from _Turicibacter_, _Finegoldia_, _Peptoniphilus_ and two OTUs from the _Anaerococcus_ genera that could distinguish lumen from mucosal samples (Figure 4C). These results indicate that there are fine differences between the different sites of the colon, and that these can be traced down to specific OTUs on each side.

@@

### Figure legends

@@

>>>>

---
title: 'Specific taxa differentiate proximal and distal microbiota in the unprepped
  human colon'
csl: mbio.csl
fontsize: 11pt
output:
  html_document: default
  pdf_document:
    includes: null
    keep_tex: yes
  word_document: default
geometry: margin=1.0in
bibliography: references.bib
---
\vspace{35mm}

@@

#### Random Forest classification models identify important OTUs on each side
To identify OTUs that were distinct at each biogeographical site, we constructed several Random Forest models built on OTU abundances. We built the first model to classify the lumen versus mucosal samples for the right and left sides, independently (Figure 4A). The constructed model used ((Xopt)) features for the right and ((Xopt)) for the left. The models performed well when classifying these samples (`r cv10f_roc_right_bs$auc` and `r cv10f_roc_left_bs$auc`, respectively). The OTUs that were most predictive of each site are identified by their greatest mean decrease in accuracy when removed from the model. For distinguishing the right lumen and mucosa, OTUs from the _Bacteriodes_, _Actinomyces_, _Psuedomonas_ and two OTUs from the _Enterobacteraceae_ genera were differentially abundant (Figure 4B). The model classifying the left lumen and mucosa identified OTUs from _Turicibacter_, _Finegoldia_, _Peptoniphilus_ and two OTUs from the _Anaerococcus_ genera that could distinguish lumen from mucosal samples (Figure 4C). These results indicate that there are fine differences between the different sites of the colon, and that these can be traced down to specific OTUs on each side.

@@

\newpage

### Figures

@@

\newpage
